Community-conditioned language models for linguistic variation

### 2021-11-29 paper/paper1.tex
first fix

For this purpose, we introduce (\cref{sec:cclm}) various 
Community-Conditioned Language Models (CCLMs for short),
which learn embedding of the communites they are conditioned on 
as a side effect of their language modeling objective.
We test which architectures best make use of the community information and 
how and in what ways the resulting embeddings are
correlated with a social network-based representation of communities(\cref{sec:embedding-analysis}).
% , and model the degree to which a
% given message $m$ is acceptable in a given community $c$, by estimating the probability
% \(P(m \mid c)\).

>>>>

For this purpose, we introduce (\cref{sec:cclm}) various
Community-Conditioned Language Models (CCLMs for short). These models
are conditioned on a vector representation (or embedding), which
varies for each community. Hence, they learn \emph{community
  embeddings}.  Even though we test which architectures best make use
of the community information, our purpose is not to improve models in
terms of perplexity. Rather we want to extract the best set of
community embeddings and test in what ways the resulting embeddings
predict the social structure of subreddits. For this purpose, we test
the correlation with a social network-based representation of
communities (\cref{sec:embedding-analysis}).

% , and model the degree to which a
% given message $m$ is acceptable in a given community $c$, by estimating the probability
% \(P(m \mid c)\).
